### 2015-11-12 postdoctoral/gamma_functions.tex
partial proof of normal product result

  \begin{definition}
    For any LOTS \(M\) with minimum element \(0\),
    let \(\nu\) be the V-map on \(M\) where \(\nu(0)=K\) and \(\nu(t)=\{t\}\)
    for \(t>0\).
  \end{definition}

  Note for \(K=M=2\) that \(\gamma=\nu\).

@@

>>>>

@@

  \newpage

  \begin{definition}
    For any \(M\) containing a point \(0\),
    let \(\nu\) be the V-map on \(M\) where \(\nu(0)=M\) and \(\nu(t)=\{t\}\)
    for \(t>0\).
  \end{definition}

  Note for \(M=2\) that \(\nu=\gamma\).

  \begin{corollary}
    \(\varprojlim\{2,\nu,L\}\cong\check L\).
  \end{corollary}

  \begin{theorem}
    If \(M\) is \(T_2\) or regular, then
    \(
      \varprojlim\{M,\nu,L\}\setminus\{\vect 0\}
        \cong
      (\check L\setminus\{\emptyset\})\times(M\setminus\{0\})
    \) with the usual product topology.
  \end{theorem}

  \begin{proof}
    Each point in \(\varprojlim\{M,\nu,L\}\setminus\{\vect 0\}\) is of the
    form \(\vect x_{A,m}\) where \(A\in\check L\setminus\{\emptyset\}\)
    and \(m\in M\setminus\{0\}\) defined by \(\vect x_{A,m}(l)=m\) for \(l\in A\)
    and \(x_{A,m}(l)=0\) otherwise.

    We claim that the bijection \(\theta(\vect x_{A,m})=\<A,m\>\) is a
    homeomorphism. Note that basic open sets of
    \(\varprojlim\{M,\nu,L\}\) are of the form \([U,F]\) where \(U(l)\) is
    an open subset of \(M\) for each \(l\in F\in[L]^{<\omega}\).

    Consider the point \(\<C,m\>\) in the basic open set \(V\times W\) in
    \((\check L\setminus\{\emptyset\})\times(M\setminus\{0\})\). Note that
    \(V\) is either of the form \((A,L]\) or \((A,B)\), and we may choose
    \(l_0\in C\setminus A\). We also may assume that \(W\) misses an open
    neighborhood \(Z\) of \(0\) as \(M\) is \(T_2\) or regular.
    In the case that \(V=(A,L]\) we let \(U(l_0)=W\).
    Then since \(l_0\in C\) and \(m\in W=U(l_0)\), it follows that
    \(\vect x_{C,m}\in[U,\{l_0\}]\).
    For any \(\vect x_{D,n}\in[U,\{l_0\}]\) we have that \(\vect x_{D,n}(l_0)=n\in W\);
    in particular, it's nonzero. So
    \(A\subsetneq (\leftarrow,l_0]\subseteq D\), putting \(D\in(A,L]=V\). Thus
    \(\theta(\vect x_{D,n})=\<D,n\>\in V\times W\).

    In the case that \(V=(A,B)\), we may also choose \(l_1\in B\setminus C\).
    We again let \(U(l_0)=W\), and we also let \(U(l_1)=Z\). Then as
    \(\vect x_{C,m}(l_0)=m\in W=U(l_0)\) and
    \(\vect x_{C,m}(l_1)=0\in Z=U(l_1)\), we have shown
    \(\vect x_{C,m}\in[U,\{l_0,l_1\}]\). For any \(\vect x_{D,n}\in[U,\{l_0,l_1\}]\),
    \(\vect x_{D,n}(l_0)\in W\) and \(\vect x_{D,n}(l_1)\in Z\).
    This shows that \(\vect x_{D,n}(l_0)=n\in W\) and \(\vect x_{D,n}(l_1)=0\), so
    \(
      A
        \subsetneq
      (\leftarrow,l_0]
        \subseteq
      D
        \subsetneq
      (\leftarrow,l_1]
        \subseteq
      B
    \), putting \(D\in(A,B)=V\). Thus
    \(\theta(\vect x_{D,n})=\<D,n\>\in V\times W\).

    On the other hand, consider the point \(\vect x_{C,m}\) in the basic
    open set \([U,F]\). It follows that \(m\in U(l)\) for all \(l\in C\cap F\),
    and \(0\in U(l)\) for all \(l\in F\setminus C\).

    TODO finish
  \end{proof}

  \newpage
